\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-26 paper.tex
Updates based on IROS2017 review comments

\subsection{Representing Alternative States of the World}

@@

Complementing the spatial representation encapsulated in the scene graph, each
world also stores the world's \emph{timeline}. This data structure is shared
and synchronised amongst the clients in the same way as the scene graph.
Clients can record both \emph{events} (duration-less states) and
\emph{situations} in the timeline, \ie states with a start time and a (possibly open-ended) end time.

Importantly, the \uwds server automatically generates a snapshot of
the scene graph whenever an event or situation is added to the timeline. The
snapshot is associated to the event, which allows clients to effectively retrieve past
states of the world. This capability is anticipated to be primarily used by \uwds clients
performing action recognition.

@@

In the common case of one client performing a full update of a single world
(with $p$ nodes) at each time step, the complexity of propagating these changes across
the network would be $O(p \times m)$. Figure~\ref{fig|performances} shows
measured propagation time for one change across 20 cascading worlds.

@@

TODO LAAS

@@

@@

Figure~\ref{fig|mummerarchitecture} illustrates the topology of
the \uwds network. A first client \textit{env\_provider} provides the environment set-up and allows to build a first \texttt{ENV} world where static objects/furnitures and walls are present. 
Then, the system cascades three worlds successively by the help of three clients. \textit{robot\_monitor} provides a first world where the robot is present. \textit{humans\_monitor} provides a new world where the humans are present. \textit{object\_monitor} provides a new world where the objects are present. At this end we obtain a world \texttt{BASE}.

This world \texttt{BASE} is then passed through a \textit{physics filter} client as explained in section \ref{physics} to obtain a \texttt{STABLE} world where all elements are present and consistent: robot, humans, objects and static environment. On this world, we use \textit{Computation of spatial relations} client to get information such as onTop, isIn or isAbove.

This world \texttt{STABLE} is then used by a \textit{perspective filter} client to provide different perspectives given the monitored agent (in our case: human 1, human 2 or the robot itself). Besides giving a view of the input world in the perspective of the monitored agent, it aggregates all the information gathered by this agent. Consequently, it does not offer a snapshot of the agent belief at a particular time but an aggregated version along the time.

@@

\subsubsection{Representation capabilities} as presented in
section~\ref{design}, the current version of \uwds allows to represent
\emph{objects}, \emph{abstract entities} like groups and \emph{perspectives}.
\emph{Fields} are also part of the \uwds design, but are not yet implemented.
Fields are commonly used to represent
continuously-valued spatial entities. Fields might or might not be spatially
bounded. Examples include the working space of a robot arm (spatially bounded),
the field of view of a camera (spatially bounded), proxemics (potentially
unbounded). We plan to represent fields in \uwds using the memory-efficient
octomaps~\cite{hornung2013octomap}. Similarly to geometric data, octomaps
will not be directly stored with the nodes (nodes will refer to them through 
handles), but unlike geometric data, they will not be treated as immutable
datasets by the server, permitting real-time updates.

>>>>

\subsection{Representing Alternative States of the World}\label{alter}

@@

Complementing the spatial representation encapsulated in the scene graph, each
world also stores the world's \emph{timeline}. This data structure is shared and
synchronised amongst the clients in the same way as the scene graph.  Clients
can record and query both \emph{events} (duration-less states) and \emph{situations} in
the timeline, \ie states with a start time and a (possibly open-ended) end time.

%Importantly, the \uwds server automatically generates a snapshot of
%the scene graph whenever an event or situation is added to the timeline. The
%snapshot is associated to the event, which allows clients to effectively retrieve past
%states of the world. This capability is anticipated to be primarily used by \uwds clients
%performing action recognition.

@@

In the common case of one client performing a full update of a single world
(with $p$ nodes) at each time step, the complexity of propagating these changes across
the network would be $O(p \times m)$. Figure~\ref{fig|performances} shows
measured propagation time for one change across up to 20 cascading worlds.

@@

When perception modules provide objects localization, the consistency is not guarantee, objects on a table seem to slightly flight in the air, when dropping them in a bin the localization is not updated any more when the objects are occulted, resulting in objects that fly just above the bin.

Being able to manage that issues by simulating the gravity is the purpose of a dedicated client  
{\tt physics filter} that have been designed using Bullet RT physics simulation and pybullet \url{https://pybullet.org/} library, it provides from an input world, an output world where objects described by an URDF file are filtered by the simulator, which gives us the near future of the objects based on their position, mass and inertia.

@@

Underworlds is used 
%within the European MuMMER project
to be able to assess visibility and knowledge about objects, places and agents within the scene.

Let's imagine a little example with two humans and a robot looking at a table. On the table there is an object that is only seen by one human and the robot (it is hidden for the second human). Figure~\ref{fig|mummerarchitecture} illustrates the topology of the \uwds network we can define for this example.

@@

A first client \textit{env\_provider} provides the environment set-up and allows to build a first \texttt{ENV} world where static objects/furnitures and walls are present. 
Then, the system cascades three worlds successively by the help of three clients. \textit{robot\_monitor} provides a first world where the robot is present. \textit{humans\_monitor} provides a new world where the humans are present (using~\cite{Khalidov_Idiap-RR-02-2017}). \textit{object\_monitor} provides a new world where the objects are present (using {\tt ar\_track\_alvar}\footnote{\url{http://wiki.ros.org/ar\_track\_alvar}). At this end we obtain a world \texttt{BASE}.

This world \texttt{BASE} is then passed through a \textit{physics filter} client as explained in section~\ref{physics} to obtain a \texttt{STABLE} world where all elements are present and consistent: robot, humans, objects and static environment. On this world, we use \textit{Computation of spatial relations} client to get information such as {\tt onTop}, {\tt isIn} or {\tt isAbove}.

This world \texttt{STABLE} is then used by a \textit{perspective filter} client to provide different perspectives given the monitored agent (in our case: human 1, human 2 or the robot itself). Besides giving a view of the input world in the perspective of the monitored agent (through the robot's own perspective), it aggregates all the information visibly gathered by this agent. Consequently, it does not offer a snapshot of the agent belief at a particular time but an aggregated estimation along the time.

With this network, we are able to assess among other things that the object on the table is seen by the robot and human 1 but not by human 2. Moreover, if human 1 moves in a position where the object becomes not visible for him, the \textit{perspective filter} will keep the knowledge about the fact that he has already seen it (and keep the last position where it has been seen).

%This knowledge could then be used by planner such as HATP to plan differently given the knowledge or ignorance of an agent regarding the environment.

We are currently setting up this kind of network in the framework of the European project MuMMER where a Pepper robot is intended to handle interactive situations in a Mall in Finland. One of the situation is a guiding task where Pepper will help people to find their route by pointing them landmarks and explaining them how to reach a destination. The use of \uwds enables to get knowledge about what the customer sees (or has seen) or not and to handle the task accordingly. We plan also to be able to add information coming from the dialogue (e.g. if the customer says that he has seen a particular landmark that could consequently be added to his belief world). Moreover, we plan also to use alternative world ability given by \uwds (as explained in \ref{alter}) (e.g. to create a world where we put the customer in front of the desired shop )would be able to infer a possible world where the customer will be put in front of the desired shop to be able to explain him what he will see at destination.

TODO LAAS: on est en train de reflechir a mettre dans l'exemple un nouvau monde simule (notre cas d'ecole c'est qu'on place le bonhomme en simule devant un magasin et on est capable de calculer ce qu'il verra en face de ce magasin) mais il faut qu'on le fasse coller avec l'exemple qu'on a

@@

\subsubsection{Representation capabilities} as presented in
section~\ref{design}, the current version of \uwds allows to represent
\emph{objects}, \emph{abstract entities} like groups and \emph{perspectives}.
\emph{Fields} are also part of the \uwds design, but are not yet implemented.
Fields are commonly used to represent
continuously-valued spatial entities. Fields might or might not be spatially
bounded. Examples include the working space of a robot arm (spatially bounded),
the field of view of a camera (spatially bounded), proxemics (potentially
unbounded). We plan to represent fields in \uwds using the memory-efficient
octomaps~\cite{hornung2013octomap} or NDT-OM maps~\cite{saarinen20133d}.
Similarly to geometric data,these datastructures
will not be directly stored with the nodes (nodes will refer to them through 
handles), but unlike geometric data, they will not be treated as immutable
datasets by the server, permitting real-time updates.
